---
title: "KoreaAddressAPI package vignette"
author: "ByeongKeon Kim"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{KoreaAddressAPI package vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r install}
# Install package from github
devtools::install_github('skysign/KoreaAddressAPI', force = TRUE)

# Install package from local directory
#devtools::install_local('C:/work_git/KoreaAddressAPI', force = TRUE)
```

```{r setup}
library(KoreaAddressAPI)
```

# Function in KoreaAddressAPI

## KAParse() fucntion

This function is to parse Korea address string as per administrative areas. KAParse read only the column which is pointed by columnName parameter, and add new columns for administrative areas such as SiDoMyeong, SiGunGuMyeong. If we can't find appropriated administrative area, we mark 'x' to its corresponding column. 

#. usage
KAParse(dfDirtyJuso, columnName)


#. parameters
`dfDirtyJuso` Input data frame

`columnName` column name of input data frame, which will be parsed

#. return
Returned data frame has new columns as corresponding administrative areas, and they have a parsed the name of particular administrative area.

#. example
```{r}
dirtyJuso = c('서울특별시 \n\t   동작구 | |   사당동',
              '서울특별시 없는구 자당동')
dfDirtyJuso = data.frame(dirtyJuso)
dfDirtyJuso

dfCleaned = KAParse(dfDirtyJuso, 'dirtyJuso')
dfCleaned
```